The Sub-Millimetre User Reduction Facility: an iterative map-maker for SCUBA-2

### 2010-11-25 smurf_paper.tex
Use unix line endings
So this changes every line in the file...
A test commit - remove a duplicated "the"
Correct symbol used to refer to common mode noise following eqn 2

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2006} is a new instrument for the the 15-m
James Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
can simultaneously image the sky in two broad bands centered over 450
and 850\,\micron. Ultimately, the instrument will also be equipped
with a Fourier transform spectrometer \citep[FTS-2,][]{gom2010}, and a polarimeter
\cite[POL-2,][]{bastien2005}. This paper describes the Submillimetre User Reduction Facility,
SMURF, a software package for reducing the imaging data, with an
emphasis on data taken during the SCUBA-2 Shared-Risks Observing period
(S2SRO) which took place from 2010 February 11 to 2010 March 25. The reduction
of FTS-2 and POL-2 data will be described at a later date once these
additional instruments have been commissioned.

@@

The primary goal of map-making is to model and remove
$\mathbf{n}^\mathrm{f}_i$ and $\mathbf{c}^\mathrm{f}_i$ from the
time-series. By re-gridding the remaining data we can then hope to
approach the theoretical noise limit in the map.

>>>>

The Submillimetre Common User Bolometer Array 2
\citep[\scuba,][]{holland2006} is a new instrument for the 15-m
James Clerk Maxwell Telescope (JCMT) on Mauna Kea, Hawai'i. The camera
can simultaneously image the sky in two broad bands centered over 450
and 850\,\micron. Ultimately, the instrument will also be equipped
with a Fourier transform spectrometer \citep[FTS-2,][]{gom2010}, and a polarimeter
\cite[POL-2,][]{bastien2005}. This paper describes the Submillimetre User Reduction Facility,
SMURF, a software package for reducing the imaging data, with an
emphasis on data taken during the SCUBA-2 Shared-Risks Observing period
(S2SRO) which took place from 2010 February 11 to 2010 March 25. The reduction
of FTS-2 and POL-2 data will be described at a later date once these
additional instruments have been commissioned.

@@

The primary goal of map-making is to model and remove
$\mathbf{n}^\mathrm{f}_i$ and $\mathbf{n}^\mathrm{c}$ from the
time-series. By re-gridding the remaining data we can then hope to
approach the theoretical noise limit in the map.
